Subtle Gestures with the J!NS MEME

### 2021-08-14 Paper/paper.tex
Begin Analysis section

% Assigned to FB
\section{Analysis}
Explaining the J!ns Meme.

What was our workflow?

Which gestures did we choose?

How does the J!ns Meme work and how do we use it?

@@

>>>>

% Assigned to FB
\section{Analysis}
% TODO introduction for analysis section
What does our research contribute? (Additional subtle gestures, ...)

% TODO, maybe do this in the Introduction section? ~FB
Explaining the J!ns Meme.

% TODO
What was our goal?

\subsection{Workflow}
We began with planning the rough outline that our research would follow.
The plan was as follows:
* Gather gesture ideas
* Check ideas for detectable responses
* Create tools to automate the recording of gestures
* Collect labelled data with the tools
* Model, train and validate a neural network until its performance is sufficient
* Test the network on our withheld test dataset

[Insert figure here]

\subsection{Gestures}
% TODO, maybe use self-made illustrations here
In the first phase, we came up with gestures we considered subtle. Early candidates were:
* Pushing your glasses up your nose [see GIF]
* A thinking pose, where you touch your chin with your thumb and your cheek with your
index finger [see GIF]
* Slow nodding [see GIF]
* Tapping the frame of the glasses [see GIF]

Since some of the gestures generated barely any responses on the EOG or the IMU readouts
[see figures with an example of a strong and a weak response],
we continued coming up with gestures until we had a total of seven gestures.
The gestures we came up with and their apparent responses can be seen in the following
table:

Pushing glasses up the nose | strong
Readjusting glasses | strong
Thinking pose | weak
Slow nodding | strong
Tilting head sideways | strong
Stroking mustache | weak
Biting lip | weak
Tapping on the nose | strong
Rubbing the nose | strong
Pushing cheek up with a finger | strong
Tapping the glasses | strong

\subsection{Tools for Recording and Labelling}
% is this something for the implementation section? ~FB
How does the J!ns Meme work and how do we use it?

@@

\subsection{Neural Network Architecture and Training}
% again - how much of this belongs to implementation? ~FB
